---
title: "Output plots in plotly"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Output plots in plotly}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  self_contained: false
  lib_dir: rmarkdown_files
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE, 
  warning = FALSE
)
```

Here are some examples to output data via `ggplot2`

```{r data set creation}
library(DCVtestkit)
# Data Creation
dilution_percent <- c(10, 20, 25, 40, 50, 60,
                        75, 80, 100, 125, 150,
                        10, 25, 40, 50, 60,
                        75, 80, 100, 125, 150)
dilution_batch <- c("B1", "B1", "B1", "B1", "B1",
                    "B1", "B1", "B1", "B1", "B1", "B1",
                    "B2", "B2", "B2", "B2", "B2",
                    "B2", "B2", "B2", "B2", "B2")
sample_name <- c("Sample_010a", "Sample_020a",
                 "Sample_025a", "Sample_040a", "Sample_050a",
                 "Sample_060a", "Sample_075a", "Sample_080a",
                 "Sample_100a", "Sample_125a", "Sample_150a",
                 "Sample_010b", "Sample_025b",
                 "Sample_040b", "Sample_050b", "Sample_060b",
                 "Sample_075b", "Sample_080b", "Sample_100b",
                 "Sample_125b", "Sample_150b")
lipid1_area_saturated <- c(5748124, 16616414, 21702718, 36191617,
                           49324541, 55618266, 66947588, 74964771,
                           75438063, 91770737, 94692060,
                           5192648, 16594991, 32507833, 46499896,
                           55388856, 62505210, 62778078, 72158161,
                           78044338, 86158414)
lipid2_area_linear <- c(31538, 53709, 69990, 101977, 146436, 180960,
                        232881, 283780, 298289, 344519, 430432,
                        25463, 63387, 90624, 131274, 138069,
                        205353, 202407, 260205, 292257, 367924)
lipid3_area_lod <- c(544, 397, 829, 1437, 1808, 2231,
                     3343, 2915, 5268, 8031, 11045,
                     500, 903, 1267, 2031, 2100,
                     3563, 4500, 5300, 8500, 10430)
lipid4_area_nonlinear <- c(380519, 485372, 478770, 474467, 531640, 576301,
                           501068, 550201, 515110, 499543, 474745,
                           197417, 322846, 478398, 423174, 418577,
                           426089, 413292, 450190, 415309, 457618)
dilution_annot <- tibble::tibble(Sample_Name = sample_name,
                                 Dilution_Batch = dilution_batch,
                                 Dilution_Percent = dilution_percent)
lipid_data <- tibble::tibble(Sample_Name = sample_name,
                             Lipid1 = lipid1_area_saturated,
                             Lipid2 = lipid2_area_linear,
                             Lipid3 = lipid3_area_lod,
                             Lipid4 = lipid4_area_nonlinear)

dilution_table <- create_dilution_table(dilution_annot,
                                        lipid_data,
                                        common_column = "Sample_Name",
                                        signal_var = "Area",
                                        column_group = "Transition_Name"
                                        )

dilution_classified <- dilution_table %>%
  summarise_dilution_table(grouping_variable = c("Transition_Name",
                                                 "Dilution_Batch"), 
                           conc_var = "Dilution_Percent",
                           signal_var = "Area"
  ) %>%
  dplyr::arrange(.data$Transition_Name) %>%
  evaluate_linearity(grouping_variable = c("Transition_Name",
                                           "Dilution_Batch"))
  
```

Here is the output of `dilution_table` and `dilution_classified` 

```{r print dilution data}
print(head(dilution_table), width = 100)
print(head(dilution_classified), width = 100)
```

We then create the plotly plots with `dilution_table` and `dilution_classified`

```{r create plotly table}
# Create a trellis table
trellis_table_orig <- create_trellis_table(dilution_table,
                                           dilution_summary = dilution_classified,
                                           grouping_variable = c("Transition_Name",
                                                                 "Dilution_Batch"),
                                           sample_name_var = "Sample_Name",
                                           dil_batch_var = "Dilution_Batch",
                                           dil_batch_col = c("#377eb8",
                                                             "#4daf4a"),
                                           conc_var = "Dilution_Percent",
                                           conc_var_units = "%",
                                           conc_var_interval = 50,
                                           signal_var = "Area",
                                           have_plot_title = TRUE)

trellis_list_orig <- trellis_table_orig$panel

```

Each plotly plot for each group can be found in the column `panel`

```{r print plotly plot}
trellis_list_orig[[1]]
trellis_list_orig[[7]]
```

To see the regression line on half the dilution points, set `plot_half_lin_reg = TRUE`

```{r create plotly table with half linear regression}
trellis_table <- create_trellis_table(dilution_table,
                                      dilution_summary = dilution_classified,
                                      grouping_variable = c("Transition_Name",
                                                            "Dilution_Batch"),
                                      sample_name_var = "Sample_Name",
                                      dil_batch_var = "Dilution_Batch",
                                      dil_batch_col = c("#377eb8",
                                                        "#4daf4a"),
                                      conc_var = "Dilution_Percent",
                                      conc_var_units = "%",
                                      conc_var_interval = 50,
                                      signal_var = "Area",
                                      have_plot_title = TRUE,
                                      plot_half_lin_reg = TRUE)

trellis_list <- trellis_table$panel

```

```{r print plotly plot with half linear regression}
trellis_list[[1]]
trellis_list[[7]]
```

Units of `conc_var` and `conc_var_interval` can be customised to suit the range of `conc_var`
You can also change the colours for your dilution batch from `dil_batch_col`

```{r create plotly table with conc customisation}
trellis_table <- create_trellis_table(dilution_table,
                                      dilution_summary = dilution_classified,
                                      grouping_variable = c("Transition_Name",
                                                            "Dilution_Batch"),
                                      sample_name_var = "Sample_Name",
                                      dil_batch_var = "Dilution_Batch",
                                      dil_batch_col = c("#377eb8",
                                                        "#4daf4a"),
                                      conc_var = "Dilution_Percent",
                                      conc_var_units = "mol",
                                      conc_var_interval = 20,
                                      signal_var = "Area",
                                      have_plot_title = TRUE,
                                      plot_half_lin_reg = TRUE)

trellis_list <- trellis_table$panel

```

```{r print plotly table with conc customisation}
trellis_list[[2]]
trellis_list[[8]]
```

The list of plotly can be output as follows using an R script:

```{r create pdf page, eval = FALSE}
create_trellis_report(trellis_table_orig,
                      trellis_report_name = "Dilution_Plot",
                      trellis_report_folder = "Dilution_Plot")

```
